---
title: "LASSO and Linear Regression"
author: "Parissa Amin"
date: "2022-10-09"
output: pdf_document
---



# Loading the data

Loading and scaling.

```{r}
library(coefplot)
library(glmnet) 
library(dplyr) 
library(ggplot2)  
library(reshape2)

x<-read.csv("D:/MultiOmics/Data/FeatVal.csv") 
rownames(x) <- x[,2]; x <- x[,-1:-2]  
x <- x[, c(names(x)[-which(names(x) == "Response")], "Response")]
x[x=="False"] <- 0 
x[x=="True"] <- 1 

x[] <- lapply(x, as.numeric)
x[,1:93] <- scale(x[,1:93] ) 
x[x=="NaN"] <- 0 
```


#Linear 
```{r}
Model<-lm(x$Response~.,data=x[,1:93])
summary(Model)
```


#LASSO

```{r}
y1<-data.matrix(x[,1:93])
y2<-data.matrix(x$Response) 

cv_model <- cv.glmnet(y1,y2, alpha = 1)
best_lambda <- cv_model$lambda.min
lasso_coef=predict(cv_model,type="coefficients",s=best_lambda)[1:93,]
nonzeroCoef<-lasso_coef[which(lasso_coef!=0)]  
nonzeroCoef<- as.data.frame(nonzeroCoef)
nonzeroCoef[,2]<- rownames(nonzeroCoef)
nonzeroCoef.m<- melt(nonzeroCoef)
```


Cross validation LASSO:  

```{r}
plot(cv_model)
```

 
```{r}
ggplot(nonzeroCoef.m,aes(x=V2,y=value,color=V2))+geom_point(size=5)+
  theme(text = element_text(size =8))+ 
  theme(axis.text.x=element_text(angle = -90, hjust = 0))

```



# Conlusion
Along side the ML and XAI model, I wanted to try two more traditional approaches to fit features to response to NAC. I used lineasr regression and and LASSO. While linear regression doesnt identify many significant features, lasso gives me 8 features that are relatively similar to the features I found to be important using SHAP values. 